Networks Matter in International Relations:\\A Latent Network Approach to Analysis

### 2017-10-22 paper/4_app.tex
tiny changes

\subsection{Replication of Reiter \& Stam (2003)}

\citet{reiter:stam:2003} examine the relationship between democracy, dictatorship and the initiation of militarized disputes.  They use directed dyads and find that dyads involving a democratic leader on the one hand and a personalist dictator on the other tend to be violent. They also discover that dictators are likely to challenge democracies, but that this is not reciprocal.  In addition, military regimes and single-party regimes are more prone to initiate disputes with democracies, than the other way around.  They use the MID data, but note that ``We code a state as having initiated a dispute if it is on `side A' of a MID, the conventional approach to coding initiation. This means that the state was on the side that took the first action in the dispute, whether that action was the threat, display, or use of force. We code joiners as initiators or targets, though the results do not change if we do not code joiners as initiators or targets. \ldots Though coding initiation will always be difficult, the `side A' variable has been widely used in past conflict scholarship (page 334).'' Independent variables are largely taken from an earlier study and focus on various encodings of regime types, contiguity, alliance, and capability measures. As is prevalent in these kinds of studies, Reiter \& Stam employ a logistic regression that includes an indicator of the time since the last dispute as well as three cubic splines. The database for this study is constructed using EUGene \citep{bennett:stam:2000} and comprises approximately three-quarters of a million stacked dyads. Based on their statistical analysis, they conclude that institutional constraints affect the propensity of democratic and non-democratic leaders to engage in military conflict.

@@

\subsection{Replication of McDonald (2004)}

@@

\subsection{Replication of Rose (2004)}

@@

\subsection{Replication of Weeks (2012)}

@@

\subsection{Replication of Gibler (2017)}

@@

Fifth, it is useful to suggest that a lot of what is \textit{known} about international relations based on studies of dyadic data should be taken with a grain of salt, and awaits a reassessment using methods that do not rely on an assumption that all the dyads are independent and identically distributed.

>>>>

\subsection{Re-estimation of Reiter \& Stam (2003)}

\citet{reiter:stam:2003} examine the relationship between democracy, dictatorship and the initiation of militarized disputes.  They use directed dyads and find that dyads involving a democratic leader on the one hand and a personalist dictator on the other tend to be violent. They also discover that dictators are likely to challenge democracies, but that this is not reciprocal.  In addition, military regimes and single-party regimes are more prone to initiate disputes with democracies, than the other way around.  They use the MID data, but note that 
\begin{quote}
We code a state as having initiated a dispute if it is on `side A' of a MID, the conventional approach to coding initiation. This means that the state was on the side that took the first action in the dispute, whether that action was the threat, display, or use of force. We code joiners as initiators or targets, though the results do not change if we do not code joiners as initiators or targets. \ldots Though coding initiation will always be difficult, the `side A' variable has been widely used in past conflict scholarship (page 334).
\end{quote} 
Independent variables are largely taken from an earlier study and focus on various encodings of regime types, contiguity, alliance, and capability measures. As is prevalent in these kinds of studies, Reiter \& Stam employ a logistic regression that includes an indicator of the time since the last dispute as well as three cubic splines. The database for this study is constructed using \texttt{EUGene} \citep{bennett:stam:2000} and comprises approximately three-quarters of a million stacked dyads. Based on their statistical analysis, they conclude that institutional constraints affect the propensity of democratic and non-democratic leaders to engage in military conflict.

@@

\subsection{Re-estimation of McDonald (2004)}

@@

\subsection{Re-estimation of Rose (2004)}

@@

\subsection{Re-estimation of Weeks (2012)}

@@

\subsection{Re-estimation of Gibler (2017)}

@@

Fifth, it is useful to suggest that a lot of what is \textit{known} about international relations based on studies of dyadic data should be taken with a grain of salt, awaiting a reassessment using methods that do not rely on an assumption that all the dyads are independent and identically distributed.
